Attempting to pull iterations out of RSiena

### 2017-01-28 iterationsfromRSiena.Rmd
can animate some microsteps

```{r examplecode}
library(RSiena)
# ---- A. ----------------------------------------------------------------------
# First we have to create objects for the dependent variables.

@@

```{r delete}
ansnullchains <- ansnullchains[,-c(1:3, 6:8, 10)]
str(ansnullchains)
# annoyingly, a lot are factors... fix it real quick.
for (i in 1:3){
  ansnullchains[,i] <- as.numeric(as.character(ansnullchains[,i]))
}
ansnullchains[,4] <- as.logical(as.character(ansnullchains[,4]))
```

@@

```{r attrs}
get_attr_info <- function(ans){

@@

>>>>

```{r examplecode, cache=TRUE}
library(RSiena)
# ---- A. ----------------------------------------------------------------------
# First we have to create objects for the dependent variables.

@@

```{r delete, cache=TRUE}
ansnullchains <- ansnullchains[,-c(1:3, 6:8, 10)]
str(ansnullchains)
# annoyingly, a lot are factors... fix it real quick.
for (i in 1:3){
  ansnullchains[,i] <- as.numeric(as.character(ansnullchains[,i]))
}
ansnullchains[,4] <- as.logical(as.character(ansnullchains[,4]))
```

@@

```{r attrs, cache=TRUE}
get_attr_info <- function(ans){

@@

What are you, `mu` and `sigma2`? Look at the [Siena Algorithms](http://www.stats.ox.ac.uk/~snijders/siena/Siena_algorithms.pdf)!

On p. 32 of this manual, there is a defining list of variables that might be our mysterious 13 list elements!!!!

1. "Aspect": 'network' or 'behavior' 
2. No idea
3. The name of the dependent variable
4. "Actor i": sending actor
5. "Actor j": receiving actor
6. "Difference": meaningless 0 when aspect is 'network'
7. ~~$a_n$ value at parameter update (??)~~ `finalReciprocalRate` attribute, whatever that is.
8. "log OptionSet probability": log probability of making a ministep of this OptionSet. Okay. This value is `r ansnull$chain[[1]][[1]][[1]][[1]][[8]]` always. Now we know it's been $\log$'d. So I'll $\exp$ it: `r exp(ansnull$chain[[1]][[1]][[1]][[1]][[8]])`. This is the probabililty of randomly selecting one node out of the 50 to be changed. CRUSHED IT.
9. "log choice probability": log probability of making a ministep of this choice. So, if we $\exp$ it, that's the probability of changing the tie from node $i$ to node $j$ given the current network stats. 
10. The `initialStateDifferences` attribute value (?)
11. The `endStateDifferences` attribute value (?)
12. No idea
13. No idea

Okay, now that I know that the `X9` variable is the log of the probability of making the tie, let's look at some plots of it when it's been exponentiated to get the probability back out.

```{r newplots}
names(ansnullchains)[1:3] <- c("actori", "actorj", "logchoiceprob")
ggplot(data= ansnullchains) + 
  geom_histogram(aes(x = exp(logchoiceprob)), binwidth = 0.025)
```

Now, let's color our tile plot from before by the mean probability of that tie (first requires some data manipulation):

```{r newplots2}
library(dplyr)
ansnullchains %>% 
  group_by(actori, actorj) %>% 
  summarize(meanprob = mean(exp(logchoiceprob))) %>% 
  arrange(actori, actorj, meanprob) -> ansnull_probs

ggplot(data = ansnull_probs) + 
  geom_raster(aes(x = actori, y = actorj, fill = meanprob)) + 
  #facet_wrap(~period, labeller = 'label_both') + 
  scale_fill_continuous(low = 'white', high = 'blue') + 
  theme(aspect.ratio = 1)
```

Cool. That's much more informative and logical.
